Induced universal graphs for families of small graphs

### 2021-10-15 paper/paper.tex
isomorphisms -> automorphisms (correction)
Start writing more about iteration orders

For those graphs $G$ that do not contain a copy of each element of $\calF(k)$,
it improves the speed of our algorithm if we can iterate over
$\calF(k)$ in an order that allows us to quickly reject $G$ by finding a graph
that is not an induced subgraph of $G$.  The approach I used was to sort
$\calF(k)$ in descending order of number of isomorphisms.  In particular, this
means that the clique $K_k$ and the independent set $I_k$ are the first two
graphs tested.

@@

>>>>

@@

\section{Iteration order for $\calF$}\label{sec:iteration-order}

When deciding whether a graph $G$ contains any element of $\calF(k)$, are
some iteration orders of $\calF(k)$ better than others?
For a graph $G$ that contains a copy of each element of $\calF(k)$, the iteration
order is of no importance; we much check every element of $\calF(k)$.
For graphs $G$ that do \emph{not} contain a copy of each element of $\calF(k)$,
however, we would like to find an order of $\calF(k)$ such that graphs
that are likely to fail the subgraph isomorphism test are checked early.

As Diaconis and Chatterjee note, \cite{chatterjee2021isomorphisms}, the complete
graph $K_n$ is the `hardest' graph for a random graph to contain.  This led me
to consider two possible orderings in which $K_k$ and its complement $I_k$ come
first.  The first of these approaches is to the sort $\calF(k)$ such that
graphs with large automorphism appear first.  The second is to place graphs
with unusually high or low edge counts, as measured by the absolute value of
${2|E(G)| - {|V(G)| \choose 2}}$, first.

\Cref{fig:scatter} considers these two strategies, using at attempt to find
an induced universal graph of order 8 $\calF(5)$ as an example. Each point
represents one of the 34 graphs of order 5; only 17 points are visible as each
graph and its complement appear in the same place on the charts.  On the vertical
axis, we have the number of graphs in $\calF(8)$ containing $G$; we would like
graphs for which this value is as small as possible to appear early in our order.
On the horizontal axes we have each of our two measures: size of automorphism group
and `extremeness' of edge count.  The latter measure has a strong correlation
with the number of graphs containing $G$ as an induced subgraph, suggesting that
it is a good proxy to use when sorting the list of graphs.

%    \subfigure[][TODO caption] {
      \includegraphics*{img/automorphisms-scatter.pdf}
%      \label{fig:scatter-a}
%    }
     \qquad
%    \subfigure[][TODO caption] {
      \includegraphics*{img/deg-scatter.pdf}
%      \label{fig:scatter-b}
%    }
    \caption{For each graph $G \in \calF(5)$, we plot on the vertical axis
    the number of graphs in $\calF(8)$ that contain $G$ as an induced subgraph.
    This value has a strong negative correlation with the size of the automorphism
    group of $G$ (left plot), but a weaker correlation with a measure of how
    extreme the edge count of $G$ is (right plot).
    All axis scales are logarithmic.}
\label{fig:scatter}
\end{figure}
